---
title: "Research Notebook"
author: "Your Name"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-summary: "Show code"
    embed-resources: true
    theme: default
    number-sections: true
  pdf:
    toc: true
    number-sections: true
    geometry: margin=1in
execute:
  cache: true
  warning: false
  message: false
  echo: true
editor: visual
---

```{r setup, include=FALSE}
#| label: setup
#| include: false

# Load required libraries
library(knitr)
library(dplyr)
library(ggplot2)
library(here)

# Set global chunk options
knitr::opts_chunk$set(
  fig.width = 8,
  fig.height = 6,
  fig.align = "center",
  out.width = "80%"
)

# Create necessary directories
if (!dir.exists("r_scripts")) dir.create("r_scripts")
```

# Introduction

## Research Questions

Describe your research questions and hypotheses here.

## Data Overview

Brief description of your dataset and variables of interest.

# Data Exploration

```{r data-structure}
#| label: fig-data-structure
#| fig-cap: "Data structure overview"
#| cache: true

# Your data exploration code here
```

## Descriptive Statistics

<details>
<summary>Click to expand descriptive statistics</summary>

```{r descriptive-stats}
#| label: fig-descriptive-stats
#| fig-cap: "Descriptive statistics"
#| cache: true

# Your descriptive statistics code here
```

</details>

# Hypothesis Testing

## Research Question 1

```{r hypothesis-1}
#| label: fig-hypothesis-1
#| fig-cap: "Analysis for research question 1"
#| cache: true

# Your hypothesis testing code here
```

# Results

## Statistical Models

```{r models}
#| label: fig-models
#| fig-cap: "Statistical models and results"
#| cache: true

# Your modeling code here
```

## Key Findings

Summarize your key findings here.

# Discussion

Interpret your results and discuss implications.

# Conclusion

Brief summary of conclusions and future directions.

# Session Information

```{r session-info}
#| label: session-info
#| echo: false

sessionInfo()
```